---
title: "Text Clustering using K-Means"
author: "HARSHITHA MEKALA"
date: "25 May 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the input file
```{r}
comments <- read.csv("C:/Users/Administrator/Downloads/saidatasets/Comments.csv")
corpus
View(comments)
head(comments)
```

## loading libraries
```{r}
library("tm")
```

## Convert into text corpus
```{r}
comments1 <- Corpus(VectorSource(comments$Feedback))
comments1
inspect(comments1)
#View(comments1)
typeof(comments1)
```

## convert to lower-case
```{r}
comments1[[1]]
comments1[[83]]
comments2 <- tm_map(comments1,tolower)
inspect(comments2)
```

## Remove stop words
```{r}
comments2[[83]]
comments3 <- tm_map(comments2,removeWords,stopwords("english"))
comments3[[83]]
inspect(comments3[[83]])
```

## Remove the punctuations
```{r}
comments4 <- tm_map(comments3, removePunctuation)
inspect(comments4[[83]])
```

## Remove the numbers
```{r}
comments5 <- tm_map(comments4, removeNumbers)
inspect(comments5[[83]])
```

## Eliminating Extra White Space
```{r}
comments6 <- tm_map(comments5, stripWhitespace)
inspect(comments6[[83]])
```

## Create a term Document Matrix
```{r}
dtm <- DocumentTermMatrix(comments6)
dtm
inspect(dtm[1:5,1:10])
inspect(dtm[10,])
```

## Finding the frequent terms
```{r}
findFreqTerms(dtm,10)
findFreqTerms(dtm,5)
```

##do tfxidf
```{r}
dtm_tfxidf <- weightTfIdf(dtm)
inspect(dtm_tfxidf[1:5,1:100])
```

## do document clustering
## k-Means(this uses euclidean distance)
```{r}
m = as.matrix(dtm_tfxidf)
View(m)
rownames(m) <- 1:nrow(m)
```

## normalize the vector so that Euclidean makes sense
```{r}
norm_eucl <- function(m) m/apply(m,MARGIN = 1, FUN = function(x) sum(x^2)^.5)
m_norm <- norm_eucl
```

```{r}
m_norm1 <- m_norm[-27,]
```

## cluster into 4 clusters
```{r}
cl <- kmeans(m_norm,4)
cl
```

```{r}
cl$cluster
cl$size
table(cl$cluster,cl$size)
```

```{r}

```

```{r}

```

```{r}

```

